### 2021-08-03 paper/localpsf.tex
method section getting ok

\begin{algorithm2e}
	\SetAlgoNoLine
	\SetKwInOut{Input}{Input}
	\SetKwInOut{Output}{Output}
	{	
		\Input{Linear operator $\Aop$, parameter $\text{max\_batches}$}
		\Output{Dirac comb responses $\{\eta^b\}_{b=1}^{\text{max\_batches}}$, \\
			weighting functions $\{w_i\}_{i=1}^r$}

		Compute spatially varying mean, $\mu$, and covariance, $\Sigma$, using Algorithm \ref{alg:varhpi_mean_cov}.

@@

			Compute $\eta^b$ by applying $\Aop$ to the dirac comb associated with $S_b$ (Section \ref{sec:get_impulse_response})

			Compute weighting functions $w_i$ using Algorithm \ref{alg:weighting_functions_incremental}. In lines 2 and 3 of Algorithm \ref{alg:weighting_functions_incremental}, only solve for $\psi_i$ and $\theta_i$ associated with new points $x_i$ in $S_b$. The functions $\psi_i$ and $\theta_i$ associated with points in previous batches have already been computed in previous iterations of this for loop.
		}

	}
	\caption{Construct product-convolution approximation $\AopPc$}
	\label{alg:construct_Atilde}
\end{algorithm2e}

@@

\begin{theorem}[Impulse response moments]
	\label{thm:vol_mean_cov}
	Let $\alpha:\Omega \rightarrow \mathbb{R}$, $\mu:\Omega \rightarrow \mathbb{R}^d$, and $\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d}$, be the following functions:
	\begin{equation*}
	\alpha(x) := \int_{\Omega} \phi_x(y) dy, \qquad
	\mu(x) := \mathbb{E}(\widehat{\phi}_x), \qquad
	\Sigma(x) := \Var(\widehat{\phi}_x),
	\end{equation*}
	where $\mathbb{E}(\widehat{\phi}_x)$ denotes the mean of $\widehat{\phi}_x$, and $\Var(\widehat{\phi}_x)$ denotes the variance of $\widehat{\phi}_x$.	Let  $x^i$ denote the $i^\text{th}$ component of $x$, i.e., $x = \left(x^1, x^2, \dots, x^d\right)$. Let $C$, $\{L^i\}_{i=1}^d$, and ${\{Q^{ij}\}_{i=1}^d}_{j=1}^d$ be the following constant, linear, and quadratic functions:
	\begin{equation*}
	C(x) := 1, \qquad
	L^i(x) := x^i, \qquad
	Q^{ij}(x) = x^i x^j.
	\end{equation*}
	Let $f/g$ to denote the pointwise division of functions, $\left(f/g\right)(x) = f(x)/g(x)$, and $f\cdot g$ to denote the pointwise multiplication of functions, $(f\cdot g)(x) = f(x)g(x)$. The following results hold:
	\begin{align*}
	\alpha =& \left(\Aop^T C\right)^* \\
	\mu^i =& \left(\Aop^T L^i\right)^* / \alpha \\
	\Sigma^{ij} =& \left(\Aop^T Q^{ij}\right)^* / \alpha - \mu^i\cdot \mu^j
	\end{align*}
	 for $i=1,\dots, d$, $j=1,\dots,d$.
\end{theorem}

@@

		$\alpha = \left(\mathcal{A}^T C\right)^*$

@@

			$\mu^i = \left(\mathcal{A}^T L^i\right)^* / \alpha$
		}
		\tcp{Compute covariance $\Sigma$}
		\For{$i=1,2,\dots,d$}{
			\For{$j=1,\dots,i$}{
				Form quadratic function $Q^{ij} = x^i x^j$

				$\Sigma^{ij} = \left(\mathcal{A}^T Q^{ij}\right)^* / \alpha - \mu^i\cdot \mu^j$

				$\Sigma^{ij} = \Sigma^{ji}$

@@

Now that we have estimates of the supports of the functions $\phi_x$, we use these estimates, combined with a greedy ellipsoid packing algorithm, to choose sets of sample points, $S_b$. These sample points will be used in Section \ref{sec:get_impulse_response} to form Dirac combs, which are then used to compute impulse responses of $\mathcal{A}$. We start with a finite set of candidate points $P$. To build a batch of sample points, $S_b$, first we initialize $S_b$ as an empty set. Then we select the point $p \in P$ that is the farthest away from all points in previous sample point batches. That is, $p$ is a maximizer of the following optimization problem:
\begin{equation*}
\max_{p \in P} \min_{x \in S_1 \cup \dots \cup S_{b-1}} \|p - x\|.
\end{equation*}
Once $p$ is selected, we remove $p$ from $P$. If $p$ is sufficiently far from all of the previously chosen points in the current batch, in the sense that $E_p \cap E_q = \{\}$ for all $q \in S_b$,
%and if $p$ is sufficiently far from the boundary, in the sense that $E_p \cap \partial \Omega = \{\}$, 
then we add $p$ to $S_b$. Otherwise we discard $p$. Recall that $E_p$ and $E_q$ are ellipsoids associated with points $p$ and $q$, respectively, as defined in \eqref{eq:support_ellipsoid}. This process repeats until there are no more points in $P$.  This is detailed in Algorithm \ref{alg:point_choice}. We determine whether $E_p \cap E_q = \{\}$ using the fast ellipsoid intersection test described in Appendix \ref{sec:fast_ellipsoid_intersection_test}.

@@

\subsubsection{Interpolation onto local regular grids}

@@

For the weighting functions, we use the smoothest functions (in a least-squares sense) that interpolate the points $x_i$. Constructing the weighting functions requires solving two Poisson PDEs per sample point $x_i$.

>>>>

\begin{algorithm2e}
	\SetAlgoNoLine
	\SetKwInOut{Input}{Input}
	\SetKwInOut{Output}{Output}
	{	
		\Input{Linear operator $\Aop$, parameter $\text{max\_batches}$}
		\Output{H-matrix $\AmatPc$ (optionally, $\AmatPcSymPlus$)}

		Compute $\alpha$, $\mu$, and $\Sigma$ using Algorithm \ref{alg:varhpi_mean_cov}.

@@

			Compute $\eta^b$ by applying $\Aop$ to the dirac comb for $S_b$ (Section \ref{sec:get_impulse_response})

		Form convolution kernels, $\varphi_{x_i}$, on regular grids (Section \ref{sec:convolution_kernel_regular_grid})

		Modify convolution kernels to address boundary artifacts (Section \ref{sec:boundary_extension})

		Compute all weighting functions $w_i$ using Algorithm \ref{alg:weighting_functions_incremental}
%		In lines 2 and 3 of Algorithm \ref{alg:weighting_functions_incremental}, only solve for $\psi_i$ and $\theta_i$ associated with new points $x_i$ in $S_b$. The functions $\psi_i$ and $\theta_i$ associated with points in previous batches have already been computed in previous iterations of this for loop.

		Form H-matrix $\AmatPc$ (Section \ref{sec:H_matrix_conversion})

		(optional) Modify $\AmatPc$ to make $\AmatPcSymPlus$ (Section \ref{sec:make_spd})

	}
	\caption{Construct product-convolution H-matrix}
	\label{alg:construct_Atilde}
\end{algorithm2e}

@@

\begin{theorem}[Impulse response moments]
	\label{thm:vol_mean_cov}
	Let $\alpha:\Omega \rightarrow \mathbb{R}$, $\mu:\Omega \rightarrow \mathbb{R}^d$, and $\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d}$, be the following functions:
	\begin{equation*}
	\alpha(x) := \int_{\Omega} \phi_x(y) dy, \qquad
	\mu(x) := \mathbb{E}(\widehat{\phi}_x), \qquad
	\Sigma(x) := \Var(\widehat{\phi}_x),
	\end{equation*}
	where $\mathbb{E}(\widehat{\phi}_x)$ denotes the mean of $\widehat{\phi}_x$, and $\Var(\widehat{\phi}_x)$ denotes the variance of $\widehat{\phi}_x$.	Let  $x^i$ denote the $i^\text{th}$ component of $x$, i.e., $x = \left(x^1, x^2, \dots, x^d\right)$. Let $C$, $\{L^i\}_{i=1}^d$, and ${\{Q^{ij}\}_{i=1}^d}_{j=1}^d$ be the following constant, linear, and quadratic functions:
	\begin{equation*}
	C(x) := 1, \qquad
	L^i(x) := x^i, \qquad
	Q^{ij}(x) = x^i x^j.
	\end{equation*}
	Let $f/g$ to denote the pointwise division of functions, $\left(f/g\right)(x) = f(x)/g(x)$, and $f\cdot g$ to denote the pointwise multiplication of functions, $(f\cdot g)(x) = f(x)g(x)$. The following results hold:
	\begin{subequations}
		\label{eq:vol_mean_var}
	\begin{align}
	\alpha =& \left(\Aop^T C\right)^* \\
	\mu^i =& \left(\Aop^T L^i\right)^* / \alpha \\
	\Sigma^{ij} =& \left(\Aop^T Q^{ij}\right)^* / \alpha - \mu^i\cdot \mu^j
	\end{align}
	\end{subequations}
	 for $i=1,\dots, d$, $j=1,\dots,d$.
\end{theorem}

@@

		Compute $\alpha = \left(\mathcal{A}^T C\right)^*$

@@

			Compute $\mu^i = \left(\mathcal{A}^T L^i\right)^* / \alpha$
		}
		\tcp{Compute covariance $\Sigma$}
		\For{$i=1,2,\dots,d$}{
			\For{$j=1,\dots,i$}{
				Form quadratic function $Q^{ij}(x) = x^i x^j$

				Compute $\Sigma^{ij} = \left(\mathcal{A}^T Q^{ij}\right)^* / \alpha - \mu^i\cdot \mu^j$

				Set $\Sigma^{ji} = \Sigma^{ij}$

@@

We use a greedy ellipsoid packing algorithm to choose sets of sample points, $S_b$, such that there is no overlap between the ellipsoids, $E_{x_i}$, associated with the sample points, $x_i$, within a batch. These sample point batches will be used in Section \ref{sec:get_impulse_response} to compute many impulse responses of $\Aop$ using only a small number of operator actions of $\Aop$. The support of $\phi_x$ is (approximately) contained in the ellipsoid $E_x$, so by applying $\mathcal{A}$ to the Dirac comb associated with all points in a batch, we will recover the impulse responses for all sample points in that batch.

We start with a finite set of candidate points $P$. To build a batch of sample points, $S_b$, first we initialize $S_b$ as an empty set. Then we select the point $p \in P$ that is the farthest away from all points in previous sample point batches. That is, $p$ is a maximizer of the following optimization problem:
\begin{equation*}
\max_{p \in P} \min_{x \in S_1 \cup \dots \cup S_{b-1}} \|p - x\|.
\end{equation*}
Candidate points for the first batch are chosen arbitrarily from $P$.
Once $p$ is selected, we remove $p$ from $P$. If $p$ is sufficiently far from all of the previously chosen points in the current batch, in the sense that $E_p \cap E_q = \{\}$ for all $q \in S_b$,
%and if $p$ is sufficiently far from the boundary, in the sense that $E_p \cap \partial \Omega = \{\}$, 
then we add $p$ to $S_b$. Otherwise we discard $p$. 
%Recall that $E_p$ and $E_q$ are ellipsoids associated with points $p$ and $q$, respectively, as defined in \eqref{eq:support_ellipsoid}. 
This process repeats until there are no more points in $P$.  This is detailed in Algorithm \ref{alg:point_choice}. We determine whether $E_p \cap E_q = \{\}$ using the fast ellipsoid intersection test described in Appendix \ref{sec:fast_ellipsoid_intersection_test}.

@@

\subsubsection{Interpolation onto local regular grids}
\label{sec:convolution_kernel_regular_grid}

@@

%For the weighting functions, we use the smoothest functions (in a least-squares sense) that interpolate the points $x_i$. Constructing the weighting functions requires solving two Poisson PDEs per sample point $x_i$.
